---
title: "Usage of dv.manager dispatchers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage of dv.manager dispatchers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## How to set up a *dv.listings* module using dispatchers

**Dispatchers** are helper functions that allow accessing data and utility functions inside module manager in a dynamic way. Refer to `?dv.manager::mm_dispatch` for more information about their functionalities. The boxes below show two examples on how they can be used to set up a *dv.listings* module. Note that it is not possible to use both arguments, `dataset_names` and `dataset_disp`, at the same time in a `mod_listings()` call.

### a. Filtered data

This code piece produces essentially the same app behavior as using the `dataset_names` argument. That is, any selection made by the user in the global filter menu affects the module display. 

```{r filtered, eval = FALSE}
dv.listings::mod_listings(
  module_id = "mod2a",
  dataset_disp = dv.manager::mm_dispatch(
    from = "filtered_dataset",
    selection = c("adsl", "adae", "adtte")
  )
)
```


### b. Unfiltered data

In case it is undesirable that global filter settings affect the listings displayed in a *dv.listings* module, it is possible to define the dispatcher such that it delivers always unfiltered data. This means that [any global filter will be ignored]{.ul}!

```{r unfiltered, eval = FALSE}
dv.listings::mod_listings(
  module_id = "mod2b",
  dataset_disp = dv.manager::mm_dispatch(
    from = "unfiltered_dataset",
    selection = c("adsl", "adae", "adtte")
  )
)
```

