<style>
.infobox {
  border: 1px solid;
  padding: 10px;
  margin: 10px 0;
}

.warning {
  border-color: #FFA07A;
  background-color: #FFE4E1;
}
</style>


```{r setup, message = FALSE}
# Import vdoc functions ----
vdoc <- local({
  #                      ##########
  # package_name is used # INSIDE # the sourced file below
  #                      ##########  
  package_name <- params[["package"]]
  utils_file_path <- system.file("validation", "utils-validation.R", package = package_name, mustWork = TRUE)
  source(utils_file_path, local = TRUE)[["value"]]
})

# Set required packages ----
suppressPackageStartupMessages(stopifnot(requireNamespace("DT")))
suppressPackageStartupMessages(stopifnot(requireNamespace("devtools")))

# Parse tests ----

tests <- as.data.frame(params[["tests"]])
tests[["validation_data"]] <- vdoc[["get_spec"]](tests[["test"]], vdoc[["specs"]])
tests[["spec_id"]] <- sapply(tests[["validation_data"]], function(x) x[["spec_id"]])
tests[["spec"]] <- sapply(tests[["validation_data"]], function(x) x[["spec"]])
tests[["spec_id_paste"]] <- vapply(tests[["spec_id"]], function(x) paste(x, collapse = "\n"), FUN.VALUE = character(1))
tests[["spec_paste"]] <- vapply(tests[["spec"]], function(x) paste(x, collapse = "\n"), FUN.VALUE = character(1))
tests[["desc"]] <- paste0("(#", seq_len(nrow(tests)), "): ", tests[["test"]])
tests[["with_spec"]] <- vapply(tests[["spec_id"]], Negate(is.null), FUN.VALUE = logical(1))

spec_tests <- tests[tests[["with_spec"]], ]
no_spec_tests <- tests[!tests[["with_spec"]], ]

declared_spec <- vdoc[["spec_id_list"]]
tested_spec <- unique(unlist(tests[["spec_id"]]))
uncovered_spec <- declared_spec[!declared_spec %in% tested_spec]
undeclared_spec <- tested_spec[!tested_spec %in% declared_spec]

spec_tests[["are_declared"]] <- sapply(spec_tests[["spec_id"]], function(x) all(x %in% declared_spec))

# Count tests in the different categories ----
mask_failed <- !!spec_tests[["failed"]] | spec_tests[["error"]]
mask_skipped <- !!spec_tests[["skipped"]]
mask_declared <- spec_tests[["are_declared"]]
n_pass_dec <- sum(!mask_failed & !mask_skipped & mask_declared)
n_fail_dec <- sum(mask_failed & mask_declared)
n_skip_dec <- sum(mask_skipped & mask_declared)
n_uncov <- length(uncovered_spec)
n_undec <- sum(!mask_declared)

render_spec_table <- function(t) {
  t <- t[trac_matrix_col]
  colnames(t) <- names(trac_matrix_col)
  t <- t[order(t[["Spec ID"]]), ]
  DT::datatable(t, options = list(dom = "ltp"), filter = list(position = "top"))
}

data_frame_by_row <- function(colnames, data) {
  n <- length(data)
  n_cols <- length(colnames)
  stopifnot(n %% n_cols == 0)
  columns <- vector("list", length = n_cols)
  for (i in 1:n_cols) columns[[i]] <- unlist(data[seq(i, n, n_cols)])
  do.call(data.frame, setNames(columns, colnames))
}

# Select columns to be included in the tables ----
trac_matrix_col <- c("Spec ID" = "spec_id_paste", "Spec" = "spec_paste", "Test Desc" = "desc", "File" = "file")

# Check that validation passes and set title ----
VALIDATION_PASSED <- n_fail_dec == 0 && n_uncov == 0 && n_undec == 0 && n_uncov == 0 # nolint

result_symbol <- if (VALIDATION_PASSED) "\U02705" else "\U274C"
title <- paste(result_symbol, params[["package"]], params[["version"]])
```

## `r title`
Date: `r format(Sys.time(), "%Y-%b-%d %H:%M:%S")`

The following document generates a report for R packages, to satisfy the criteria of a "Released" status under the **Non-GxP** project. The QC report contains the following information:

- **Specifications (specs):** These can be attached to every test that the user adds.
- **Traceability matrix:** Contains test cases with passed, failed, or skipped expectations.
- **Uncovered or undeclared specs**
- **Session Info and System Configuration**

::: {.infobox .warning}
Please be advised that the QC report generated for this module does not imply validation according to any other GxP criteria. 
The QC report only satisfies our internally developed quality checks for non-GxP criteria.
For clinical reporting purposes, it is essential to note that any outputs generated using this module must be checked and verified within a validated system that adheres to the appropriate GxP guidelines.
:::

----
# Traceability matrix

In this traceability matrix only those tests that point to an specification are included.

Test cases can contain several expectations a test is considered:

  - **passed** if all expectations in the test pass.

  - **failed** if at least one expectation in the test fails.

  - **skipped** if at least one expectation in the test is skipped.

A test can be both **failed** and **skipped**.

## Summary

```{r summary}
data_frame_by_row(
  colnames = c("Spec Exists", "Test", "Count", "color"),
  data = list(
    "Yes", "Pass", n_pass_dec, "white",
    "Yes", "Failed", n_fail_dec, if (n_fail_dec > 0) "red" else "green",
    "Yes", "Skipped", n_skip_dec, if (n_skip_dec > 0) "red" else "green",
    "Yes", "No Test", n_uncov, if (n_uncov > 0) "red" else "green",
    "No", "NA", n_undec, if (n_undec > 0) "red" else "green"
  )
) |>
  DT::datatable(
    rownames = FALSE,
    options = list(columnDefs = list(list(visible = FALSE, targets = c(3))), dom = "tp"),
    filter = list(position = "top")
  ) |>
  DT::formatStyle(
    c("Count"),
    valueColumns = "color",
    backgroundColor = DT::JS("value")
  )
```

## Passed tests

```{r passed_test}
render_spec_table(spec_tests[!mask_failed & !mask_skipped & mask_declared, ])
```

## Failed tests

```{r failed_test}
render_spec_table(spec_tests[mask_failed & mask_declared, ])
```

## Skipped tests

```{r skipped_test}
render_spec_table(spec_tests[mask_skipped & mask_declared, ])
```

## Uncovered specifications

```{r uncovered_spec, echo=FALSE}
data.frame("Uncovered Specifications" = uncovered_spec) |>
  DT::datatable(
    options = list(dom = "ltp"),
    filter = list(position = "top")
  )
```

## Undeclared specifications

This should always be empty, as non existant specs are controlled during test execution.

```{r undeclared_spec, echo=FALSE, results = "asis"}
render_spec_table(spec_tests[!mask_declared, ])
```

# Session Info and System Configuration

```{r system_conf}
devtools::session_info()
```

# List of specifications
```{r spec_list}
j <- vapply(
  vdoc[["spec_id_list"]],
  function(x) {
    eval(
      str2expression(
        paste0("vdoc[[\"specs\"]]$", x)
      )
    )
  },
  FUN.VALUE = character(1)
) |>
  gsub("\n", "</br>", x = _, fixed = TRUE)

data.frame(spec_id = names(j), spec = j) |>
  DT::datatable(
    rownames = FALSE,
    options = list(
      dom = "ltp"
    ),
    filter = list(position = "top"),
    escape = FALSE
  )
```
